Formalization of Abstract Rewriting

### 2025-02-23 Relations/Paper/Definitions.tex
definition underlined.

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CRs_R$] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[$a \in \FB$] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
    \end{description}
\end{definition}

>>>>

\subsection{Confluence (\texttt{ARS-Properties.agda})}
\begin{definition} The following definitions relate to confluence.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[\ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
    \end{description}
\end{definition}

### 2025-02-23 Relations/Paper/Formalization.tex
definition underlined.

\subsubsection{Theorem 1.2.3}
The following definition is required for this theorem.
\begin{definition}\hfill
    \begin{description}
        \item[$a \in CP_R$] \emph{$a$ has the cofinality property} if there exists a 
        (not necessarily strictly) increasing sequence starting from $a$ such that every
        reduct of $a$ reduces to some element of the sequence.
    \end{description}
\end{definition}

>>>>

\subsubsection{Theorem 1.2.3}
The following definition is required for this theorem.
\begin{definition}\hfill
    \begin{description}
        \item[\ule{$a \in CP_R$}] \emph{$a$ has the cofinality property} if there exists a 
        (not necessarily strictly) increasing sequence starting from $a$ such that every
        reduct of $a$ reduces to some element of the sequence.
    \end{description}
\end{definition}

### 2025-02-23 Relations/Paper/Implications.tex
definition underlined.

\begin{definition}\label{def:mf} \hfill
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SMseq_R$] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
        an $i \in \nat$ such that $s (i) \in \MF$. 
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
        definition is to be understood inductively).
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.

>>>>

\begin{definition}\label{def:mf} \hfill
    \begin{description}
        \item[\ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[\ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[\ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists 
        an $i \in \nat$ such that $s (i) \in \MF$. 
        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This 
        definition is to be understood inductively).
        \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
